Predicting instabilities of a tuneable ring laser with an iterative map model

### 2020-11-26 Papers/Journal/Cavity.tex
Finished rewriting, proper draft finished!

% Gain
\draw (0.5,2.25) circle (0.5cm);
\draw (0.5,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Er-Doped \\ Fibre};
\draw (0.5,1.75) circle (0.5cm);

@@

% Coupler and output
\draw[-stealth] (3,4) -- (3,5.5) node [pos=0.75,anchor=west,xshift=0.25cm] {Laser Output};
\draw[densely dashdotted] (2.5,3.5) -- (3.5,4.5) node [pos=1,anchor=north,yshift=-0.75cm,align=center] {Optical \\ Coupler};

@@

\filldraw[fill=white, draw=black] (0,4) circle (0.5cm) node [anchor=south,align=center,yshift=0.5cm] {Optical Circulator};
\draw[->,>=stealth] (0,4.325) arc (90:360:0.325cm);

% Arrows
\draw [->,>=stealth,domain=20:70] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
\draw [->,>=stealth,domain=110:160] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
\draw [->,>=stealth,domain=110:160] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
\draw [->,>=stealth,domain=200:250] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
\draw [->,>=stealth,domain=200:250] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
\draw [->,>=stealth,domain=290:340] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});

@@

% Arrows
%\draw[-stealth] (2.16,0) -- (2.15,0);
%\draw[-stealth] (2.39,4) -- (2.4,4);
%\draw[-stealth] (6.76,0) -- (6.75,0);
%\draw[-stealth] (7.09,4) -- (7.1,4);
%\draw[-stealth] (-0.649,0) -- (-0.65,0);
%\draw[-stealth] (-0.351,4) -- (-0.35,4);
\end{tikzpicture}

>>>>

% Gain
\draw (0.5,2.25) circle (0.5cm);
\draw (0.5,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Er-doped \\ fibre};
\draw (0.5,1.75) circle (0.5cm);

@@

% Coupler and output
\draw[-stealth] (3,4) -- (3,5.5) node [pos=0.75,anchor=west,xshift=0.25cm] {Laser output};
\draw[densely dashdotted] (2.5,3.5) -- (3.5,4.5) node [pos=1,anchor=north,yshift=-0.75cm,align=center] {Optical \\ coupler};

@@

\filldraw[fill=white, draw=black] (0,4) circle (0.5cm) node [anchor=south,align=center,yshift=0.5cm] {Optical circulator};
\draw[->,>=stealth] (0,4.325) arc (90:360:0.325cm);

% Arrows
\draw [->,>=stealth,domain=20:70,blue] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
\draw [->,>=stealth,domain=110:160,red] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
\draw [->,>=stealth,domain=110:160,blue] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
\draw [->,>=stealth,domain=200:250,blue] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
\draw [->,>=stealth,domain=200:250,red] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
\draw [->,>=stealth,domain=290:340,blue] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});

\draw [->,>=stealth,domain=270:360,blue] plot ({2.325+0.5*cos(\x)}, {4.675+0.5*sin(\x)});
\draw [->,>=stealth,blue] (2.125, 4.675-0.5) -- (2.325+0.6, 4.675-0.5);

@@

\end{tikzpicture}
